Really Hard Instances for the Subgraph Isomorphism Problem

### 2015-09-15 paper/paper.tex
More picturation

\begin{figure*}
    \hskip-1.2cm\input{gen-graph-sat.tex}
    \setlength{\abovecaptionskip}{-2em}
    \caption{Behaviour of other solvers on the induced variant on smaller graphs, shown in the style of
        \cref{figure:induced}. The second row shows the number of search nodes used by the Glasgow
        algorithm, and the third row shows the number of decisions made by the Glucose SAT solver.}
\end{figure*}

>>>>

\begin{figure*}
    \hskip-1.2cm\input{gen-graph-sat.tex}
    \setlength{\abovecaptionskip}{-2em}
    \caption{Behaviour of other solvers on the induced variant on smaller graphs, shown in the style of
        \cref{figure:induced}. The second row shows the number of search nodes used by the Glasgow
        algorithm, the third row shows the number of decisions made by the Glucose SAT solver, and
        the third row shows the number of search nodes used by a clique encoding.}
\end{figure*}
